---
title: "Flexible Report Generation"
subtitle: "Demonstration Session, NCME 2022 Annual Meeting"
author: "Adam R. VanIwaarden"
date: April 23, 2022
knit: pagedown::chrome_print
client_city: San Diego
client_state: CA
client_organization: "The National Council on Measurement in Education"
client_name: "Derek C. Briggs, Ph.D."
project_team: "Team SGP"
project_code: "[Github](https://github.com/CenterForAssessment/NCME_2022_Project)"
project_email: avaniwaarden@nciea.org
acknowledgements: "our partners and colleagues at the Center for Assessment"
output:
  pagedown::html_paged:
    css:
    - assets/css/nciea-style.css
    - assets/css/nciea-page.css
    - assets/css/nciea-default.css
    template: assets/pandoc/nciea.html
    toc: yes
    toc_depth: 2
    self_contained: yes
    number_sections: no
    fig_caption: yes
    includes:
      in_header: assets/js/meta_lof_js.html
customjs: assets/js/lof.js
abstract: |-
  ```{r child = 'assets/rmd/pagedown/abstract.Rmd'}
  ```
---

# Why Be Flexible?

```{r rpt-gen-readme1, echo=FALSE, results="asis"}
  read.me.top <- readLines("../../../README.md")
  cat(
read.me.top[4:length(read.me.top)], sep = "\n")
```

#  Five steps to report generation

```{r rpt-gen-readme5, echo=FALSE, results="asis"}
  read.me.doc <- readLines("README.md")
  cat(
read.me.doc[12:length(read.me.doc)], sep = "\n")
```

```{r rpt-gen-step1, echo=FALSE}
  knitr::spin_child("1_Repo_Setup_and_Maintenance.R")
```

```{r rpt-gen-step2, echo=FALSE}
  knitr::spin_child("2_Report_Data.R")
```

```{r rpt-gen-step3, echo=FALSE}
  knitr::spin_child("3_Report_Analyses.R")
```

#  The Universality of Meta-Data

Before turning to Step 4, it may be useful to first look at the Universal Content
on which this step interacts. In the "*Universal_Content/Meta_Data*" directory
there are two files that contain a running list of the elements and resources that
are available and/or required for the report generation in Step 5. The purpose of
Step 4 is to combine the generic meta-data with the custom meta-data in hopes of
making a complete picture of what the report will be.

```{r rpt-gen-readmeta, echo=FALSE, results="asis"}
  read.meta <- readLines("../../../Universal_Content/Meta_Data/README.md")
  cat(
read.meta[11:length(read.meta)], sep = "\n")
```

```{r rpt-gen-step4, echo=FALSE}
  knitr::spin_child("4_Make_Configs.R")
```

```{r rpt-gen-step5, echo=FALSE}
  knitr::spin_child("5_Make_Report.R")
```

# The End

Hope that gets you started! There is a lot to dig into and we will do our best to
help you out and answer any questions.
