---
title: "Appendix B"
subtitle: "Initial SGP Analysis"
appendix-prefix: "B"
output:
  html_document:
    template: ../../../Universal_Content/rmarkdown/assets/pandoc/wp_appendix.html
    self_contained: true
---

```{r setup-appndx-B, echo=FALSE, include=FALSE}
  ###   set a global knitr options
  knitr::opts_chunk$set(
    cache = FALSE,
    message = FALSE,
    dev = "svg",
    fig.topcaption = TRUE,
    fig.cap = TRUE)

  knitr::knit_hooks$set(class = function(before, options, envir) {
    if(before){
      sprintf("<div class = '%s'>", options$class)
    }else{
      "</div>"
    }
  })

  fig.out.ex <- 'data-prefix="Figure"'
  tab.out.ex <- 'style="display: none;" data-prefix="Table"'

  ###   Load some R packages and functions required for HTML table creation silently.
  ###   Load SGP and other packages here to avoid messages.
  require(ymlthis)
	require(data.table)
  require(SGP)

  ###   Set Table, Figure and Equation Counters
  # startAppendix()
  setCounters()
  options(table_counter=FALSE)
  options(table_num_str = "B%d") # Prepend Appendix Letter when using tblNum()
  options(table_counter_str = paste0("**Table ", "B", "%s:**")) # "**Table A%s:**" LETTERS[appendix.number]
  options(fig_num_str = "B%d") # Prepend Appendix Letter when using figNum()
  options(fig_caption_no_sprintf = paste0("**Figure ", "B", "%d:** %s")) # "**Figure A%d:** %s"

  ###   Utility function - Assumes first two "levels" are the main dichotomy
  ord <- function(x) { # <sup>th</sup>
    o <- toOrdinal::toOrdinal(x)
    return(paste0(x, "<sup>", substr(o, nchar(o)-1, nchar(o)),"</sup>"))
  }

  "%w/o%" <- function(x,y) x[!x %in% y]

```

This appendix presents and explains the code used to conduct the "initial" Student
Growth Percentiles (SGP) analyses. These analyses are a minimal representation of
the annual analyses conducted for our client states. Only baseline SGPs are created
and SGP projections and targets (both cohort and baseline referenced) are omitted.
The goal of this step is simply to create Baseline SGPs and merge them into the
longitudinal data so that we can proceed with investigating academic impact.

```{r ida-data-prep, echo=FALSE}
  knitr::spin_child("State_A_Data_LONG.R")
```

```{r ida-sgp-analysis, echo=FALSE}
  knitr::spin_child("State_A_Baseline_SGP_Analyses.R")
```

<div class='pagebreak'> </div>

```{r  child = '../../../Universal_Content/rmarkdown/Child_RMD/Appendix_GoFit_Intro.Rmd', eval=TRUE}
```

<div class='pagebreak'> </div>

```{r  child = 'Appendix_GoFit_Grade_Level.Rmd', eval=TRUE}
```

<!--  End appendix format: re-start counters and change back to numeric for subsequent re-rendering-->

```{r, cache=FALSE, results='asis', echo=FALSE}
	options(table_counter_str = NULL)
	options(table_num_str = NULL)
	options(fig_caption_no_sprintf = NULL)
	options(fig_num_str = NULL)
```
