## Background

Beginning in spring 2020, the COVID-19 pandemic has interrupted normal school
activities and has led to unprecedented changes in the ways in which we educate
our students. Even now in spring 2021 the majority of students in the United
States continue to experience substantial impacts to their education.

This report is part of the due diligence being conducted by the `r params$state.org`
(`r params$state.org.abv`) to quantify the academic impact students in `r params$state.name`
have experienced over the year-long course of the pandemic.

Figure `r figNum(1)` illustrates how learning loss might be measured by interim
assessments taken at multiple points in an academic year. In this sentence we use
the `figNum` function to get the figure number of the next figure.  Since it has
not been placed in the report yet, we need to advance the counter by one - `figNum(1)`.

```{r, ll-interim, fig.cap = "Example image placement: learning loss interim assessment illustration", out.width="80%", fig.align='center', out.extra=fig.out.ex, results="asis"}

	if (tolower(params$render.format) == "bookdown") {
		tmp.fig.caption <- knitr::opts_current$get("fig.cap")
		cat(gsub("</p>\n", "</div>", gsub("<p>", "<div class='caption'>", markdown::markdownToHTML(text=Gmisc::figCapNo(tmp.fig.caption), fragment.only=TRUE))))
	} else fig.incr <- figNumIncrement() # Advance counter for pagedown
	knitr::include_graphics(file.path(getPath(params$unvrsl.rmd.path, "../.."), "assets", "images", "example_figure_1.png"), dpi=150, error = FALSE)
```

As Figure `r figNum()` shows, interim assessments occur at multiple time points
during the year.  This sentence shows how the `figNum` function works in more
detail (the figure increment is 0 to get the last figure number.)

Figure `r figNum(1)` illustrates how learning loss might be measured by annual
state summative assessments taken at the end of an academic year.

```{r, ll-sumative, fig.cap = "Example learning loss illustration with a summative state assessment", out.width="80%", fig.align='center', out.extra=fig.out.ex, results="asis"}

	if (tolower(params$render.format) == "bookdown") {
		tmp.fig.caption <- knitr::opts_current$get("fig.cap")
		cat(gsub("</p>\n", "</div>", gsub("<p>", "<div class='caption'>", markdown::markdownToHTML(text=Gmisc::figCapNo(tmp.fig.caption), fragment.only=TRUE))))
	} else fig.incr <- figNumIncrement() # Advance counter for pagedown
	knitr::include_graphics(file.path(getPath(params$unvrsl.rmd.path, "../.."), "assets", "images", "example_figure_2.png"), dpi=300, error = FALSE)
```

The figure counter is now at `r figNum()`: should be 2.
