## Assessment Participation

This section gets at missing data through participation rates.  Some data may need
to be provided by the state.  Another way to get at it would be to check SGP
calculation rates.  This assumes that students we had in the 2019 data should be
present in the 2021 data.  It may be the best we can do...

Table `r tblNum(1)` provides frequencies and proportions associated with student
SGP counts by year, content area, and grade. An important aspect of Table `r tblNum(1)`
is that there are no `r skip.excluded.grade` SGPs because no prior score exists with
which to calculate growth since there is no exam administered two grades prior.
The absence of SGPs for an entire grade level has a significant impact on
comparisons done at the elementary school level.

```{r, eval=ifelse(tolower(params$render.format) == "nciea", FALSE, TRUE)}
	rgroup.indx <- diff(c(which(SGP_Counts[,1] != ""), (nrow(SGP_Counts)+1)))
	tmp.caption <- "Baseline SGP counts and percentages for 2019 and 2021 by content area and grade"

  knitr::knit_print(
		htmlTable::htmlTable(SGP_Counts,
			title="", align=paste0('cc', paste(rep('r', ncol(SGP_Counts)-2), collapse="")), # rnames = tmp.rnames,
			tspanner=rep("", length(rgroup.indx)), n.tspanner=rgroup.indx,
			# tspanner=rep("", nrow(SGP_Counts)/2), n.tspanner=rep(2, nrow(SGP_Counts)/2),
			# rgroups=list(c("ELA", "Mathematics"), ""), n.rgroups=list(nrow(SGP_Counts)/2, rep(2, nrow(SGP_Counts)/2)), # n.tspanner
	    # n.cgroup=c(3, 2, 2), cgroup=c("", "Baseline", "Cohort"),
			n.cgroup=c(4, 2), cgroup=c("", "Baseline"),
	    caption=tblCap(tmp.caption)))
```

```{r, example-table-1, fig.cap="Baseline SGP counts and percentages by year, content area and grade", out.width="0", out.height="0", out.extra='style="display: none;" data-prefix="Table"', results="asis", eval=ifelse(tolower(params$render.format) == "nciea", TRUE, FALSE)}
rgroup.indx <- diff(c(which(SGP_Counts[,1] != ""), (nrow(SGP_Counts)+1)))

###  Include VERY small, transparent image to create table title and
	knitr::include_graphics("data:image/gif;base64,R0lGODlhAQABAIAAAAAAAP///yH5BAEAAAAALAAAAAABAAEAAAIBRAA7", dpi=NA, error = FALSE)

  knitr::knit_print(
		htmlTable::htmlTable(SGP_Counts,
			title="", align=paste0('cc', paste(rep('r', ncol(SGP_Counts)-2), collapse="")),
			tspanner=rep("", length(rgroup.indx)), n.tspanner=rgroup.indx,
			n.cgroup=c(4, 2), cgroup=c("", "Baseline"),
	    caption=tblCap(knitr::opts_current$get("fig.cap")))) # , css.table="margin-top: -1.25em;margin-bottom: 1em;min-width: 75%;"
```

Arcu dolor at nullam sed torquent tellus non. Cubilia eget in nisi, penatibus aenean
congue lorem et ornare tristique leo facilisi orci vel. Non varius vestibulum nam
morbi pe llentesque sit. Vitae in eget eu sed elit, et ad lacus, eleifend nisl,
potenti eget egestas. Eros eu porttitor, tristique fames, et pellentesque lacinia
et. Porttitor in etiam ac nec montes. Ante finibus purus neque ante et. Et amet
suspendisse potenti at bibendum vivamus bibendum sapien. Eget egestas pharetra
metus phasellus volutpat non donec sed id.
