## Impact on achievement

Here is an example of how to include tables for counter/caption similar to figures
in `pagedown` template.  Adam has been unable to put this into a function because
the `include_graphics` function does not play well with environments other than
the top level.  It also can NOT be done with `knitr::knit_child`.  However, this
solution seems pretty clean and lets us render the table the same way in `bookdown`
and `pagedown` with a single process.  Its a little convoluted with the requirement
of the invisible gif and the "figtab" class requirement, but I'm happy with where
it is at.

```{r, hist-prof, fig.cap="Historical percent proficient trends by content area and grade", out.width="0", out.height="0", out.extra=tab.out.ex, class = "figtab", results="asis"}
  rgroup.indx <- diff(c(which(hist_pctprf[,1] != ""), (nrow(hist_pctprf)+1)))
  # tmp.caption <- "Historical percent proficient trends by content area and grade"

	###  Include VERY small, transparent image to create table title and
	knitr::include_graphics("data:image/gif;base64,R0lGODlhAQABAIAAAAAAAP///yH5BAEAAAAALAAAAAABAAEAAAIBRAA7", dpi=NA, error = FALSE)

  knitr::knit_print(
		htmlTable::htmlTable(hist_pctprf,
			tspanner=rep("", length(rgroup.indx)), n.tspanner=rgroup.indx,
	    caption = tblCap(knitr::opts_current$get("fig.cap"))))
```

```{asis, echo = params$imputations}
Given the number of students missing in `r params$state.name`, multiple imputation
analyses were conducted to provide estimates of what the pandemic's impact might
have been if all students had participated. [Table `r tblNum(1)`](#fig:pct-prof-imputed)
provides a comparison of the observed (with missing students) and estimated (based
on multiple imputation analysis results) percent proficient results for 2021.
```

```{r, pct-prof-imputed, fig.cap="Observed versus estimated 2021 percent proficient by content area and grade", out.width="0", out.height="0", out.extra=tab.out.ex, class = "figtab", results="asis", eval = params$imputations}
  rgroup.indx <- diff(c(which(imp_pctprf[,1] != ""), (nrow(imp_pctprf)+1)))
  # tmp.caption <- "Observed versus estimated 2021 percent proficient by content area and grade"

	###  Include VERY small, transparent image to create table title and
	knitr::include_graphics("data:image/gif;base64,R0lGODlhAQABAIAAAAAAAP///yH5BAEAAAAALAAAAAABAAEAAAIBRAA7", dpi=NA, error = FALSE)

  knitr::knit_print(
		htmlTable::htmlTable(imp_pctprf,
			tspanner=rep("", length(rgroup.indx)), n.tspanner=rgroup.indx,
	    caption = tblCap(knitr::opts_current$get("fig.cap"))))
```

```{asis, echo = params$imputations}
Integer nisl maecenas nec arcu odio tortor mauris, commodo. Morbi, cubilia risus
pulvinar vestibulum cubilia malesuada. Facilisi nec tristique in facili sis
tincidunt et dictumst rutrum cum. Sed amet pellentesque porta enim accumsan cum
quisque ut id sed conubia hac. Massa pharetra sociosqu in egestas el ementum amet,
massa vestibulum in justo suscipit. Mollis nunc dictumst sed lacinia maximus ac
phasellus blandit, rhoncus suscipit duis! Arcu cum tortor velit habitasse vehicula,
nascetur viverra fames ac. Hac litora in, nisi tempor et. Purus dictum porttitor
ultricies diam ut a proin egestas. Molestie nec sed nibh lacinia ultrices malesuada
amet sociosqu.
```
