
```{r  child = '../../../Universal_Content/rmarkdown/Child_RMD/params.Rmd', eval=TRUE}
```

```{r  child = '../../../Universal_Content/rmarkdown/Child_RMD/setup_sgp_appendix.Rmd', eval=TRUE}
```

# Initial SGP Analysis {.unlisted .unnumbered}

This appendix presents and explains the code used to conduct Student Growth
Percentiles (SGP) analyses. These analyses are a minimal representation of the
annual analyses conducted for our client states.

The first section deals with data cleaning and prep, as well as simulation of
academic impact. In State A, a relatively minor amount of impact is added to the
unperturbed data. Impact is also simulated to increase as a function of prior
achievement (i.e., students with higher 2019 scores are impacted more).

In the second section we run baseline SGP analyses. Unlike typical analyses, only
baseline referenced SGPs are created and SGP projections and targets (both cohort
and baseline referenced) are omitted. The goal of this step is simply to create
Baseline SGPs and merge them into the longitudinal data so that we can proceed
with investigating academic impact.

Finally, we present goodness of fit plots for both 2019 and 2021 results. Because
the baseline was established with the 2019 cohort, this allows for a direct
comparison between pre-pandemic results and 2021 impact (based on expected or
typical growth prior to the pandemic).


```{r ida-data-prep, echo=FALSE}
  knitr::spin_child("State_A_Data_LONG.R")
```

```{r ida-sgp-analysis, echo=FALSE}
  knitr::spin_child("State_A_Baseline_SGP_Analyses.R")
```

```{r child = '../../../Universal_Content/rmarkdown/Child_RMD/Appendix_GoFit_Intro.Rmd', eval=TRUE}
```

```{r child = '../../../Universal_Content/rmarkdown/Child_RMD/Appendix_GoFit_Grade_Level.Rmd', eval=TRUE, warning = FALSE}
```

<!--  End appendix format: re-start counters and change back to numeric for subsequent re-rendering-->

```{r, cache=FALSE, results='asis', echo=FALSE}
	options(table_counter_str = NULL)
	options(table_num_str = NULL)
	options(fig_caption_no_sprintf = NULL)
	options(fig_num_str = NULL)
```
